Game Theory based Peer Grading Mechanisms for MOOCs

### 2014-12-30 Paper.tex
Small Changes
Made some small changes to the addresses and the acknowledgements
section
More small changes to acknowledgements

\numberofauthors{5}
\author{
  \alignauthor William Wu\\
    \affaddr{Acton Boxborough Regional High School}\\
    \affaddr{36 Charter Rd Acton, MA 01720, USA}\\
    \email{willy.vvu@gmail.com}
  \alignauthor Nicolaas Kaashoek\\
    \affaddr{Lexington High School}\\
    \affaddr{251 Waltham Street, Lexington, MA 02421, USA}\\
    \email{nick.kaashoek@gmail.com}
}

@@

\subsection{Additional Authors}
Mentors \newline
\textbf{Matt Weinberg} smweinberg@csail.mit.edu \newline
\textbf{Christos Tzamos} ctzamos@gmail.com

Professor \newline
\textbf{Costis Daskalakis} costis@csail.mit.edu

>>>>

\numberofauthors{2}
\author{
  \alignauthor William Wu\\
    \affaddr{Acton Boxborough Regional High School}\\
    \affaddr{36 Charter Rd\\ Acton, MA 01720, USA}\\
    \email{willy.vvu@gmail.com}
  \alignauthor Nicolaas Kaashoek\\
    \affaddr{Lexington High School}\\
    \affaddr{251 Waltham Street\\ Lexington, MA 02421, USA}\\
    \email{nick.kaashoek@gmail.com}
}

@@

\subsection{Additional Authors}
Mentors \newline
\textbf{Matthew~Weinberg}~(\href{mailto:smweinberg@csail.mit.edu}{smweinberg@csail.mit.edu})\newline
\textbf{Christos~Tzamos}~(\href{mailto:ctzamos@gmail.com}{ctzamos@gmail.com})

Advisor \newline
Professor \textbf{Costis~Daskalakis}~(\href{mailto:costis@csail.mit.edu}{costis@csail.mit.edu})
